\vspace{1.0cm} \LARGE \bf Reassortment between influenza B lineages and the emergence of a co-adapted PB1-PB2-HA gene complex

### 2014-02-05 fluB.tex
Found semi-serious labeling errors.
Got mixed up with PB1/PB2 labels in the subtype maps (occurred quite
early on).
Looks like the right trees were run but PB1 and PB2 labels were
switched. It only affects the visibility of PB1-PB2 reassortants on
trees when using discrete traits though, so nothing has to be redone.

Also including the genomic trees grid figure for supplementary info.

We have identified 3 instances of mixed-lineage PB1-PB2-HA reassortants from the data with the following PB1-PB2-HA constellations: VVY (B/Bankok/163/1990-like, 13 sequences isolated 1990 -- 5 Jan 1995), YVV (B/Nanchang/630/1994-like, 2 sequences isolated 1994 -- 1996) and YVY (B/New York/24/1993-like, 2 sequences isolated 8 Jan 1993 -- 1994).
An additional instance of reassortants with a YYV PB1-PB2-HA constellation (B/Waikato/6/2005-like, 16 sequences isolated 9 June -- 12 November in 2005) was discovered when investigating a larger dataset with only PB1, PB2, HA and NA sequences.

>>>>

We have identified 3 instances of mixed-lineage PB1-PB2-HA reassortants from the data with the following PB1-PB2-HA constellations: VVY (B/Bankok/163/1990-like, 13 sequences isolated 1990 -- 5 Jan 1995), VYV (B/Nanchang/630/1994-like, 2 sequences isolated 1994 -- 1996) and VYY (B/New York/24/1993-like, 2 sequences isolated 8 Jan 1993 -- 1994).
An additional instance of reassortants with a YYV PB1-PB2-HA constellation (B/Waikato/6/2005-like, 16 sequences isolated 9 June -- 12 November in 2005) was discovered when investigating a larger dataset with only PB1, PB2, HA and NA sequences.
